Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-10 ms.tex
Yeah

We conclude this case study with a series of simulations of the system described above for different densities.
Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in Fig. \ref{fig:velocity_profile1}.
All these plots are now merged into a final figure which is shown in Fig. \ref{fig:velocity_profiles}.
It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
As mentioned earlier, this is called the Klinkenberg effect \citep{klinkenberg1941permeability}.

\section{\label{sec:future}Future work}

Atomify continues in heavy development and we have several features planned for
future versions.
We already have a simple version of Atomify in the web browser using WebGL and WebAssembly.
This makes it easy to test scripts in the browser with all simple functionalities available.
This is especially useful in educational settings where teachers wish to introduce students
to LAMMPS without installing additional software.
It will also serve as a nice demonstration of the full desktop application of
Atomify.

Performance improvements are planned by for instance using geometry shaders in
the rendering pipeline.
This allows a fourfold reduction in the number of vertices passed from the CPU
to the GPU.
Further, geometry shaders can be used for certain modifiers,
such as the periodic copies, which are currently performed on the CPU.

% TODO Reference to KOKKOS
We also aim to include more LAMMPS backends, such as KOKKOS, and running
simulations on computing clusters while visualizing them on the users own
computers.

The script editor will get features such as autocompletion of LAMMPS commands
and easy access to the online documentation by hovering or selecting specific
commands.

We are also working on including Moltemplate and other programs that generate
systems to make it easier for users to get started with more complex
simulations.

\section{Availability}

Atomify is availabe on Linux, MacOS and Windows and can be downloaded from
\href{https://ovilab.net/atomify}{http://ovilab.net/atomify}.
A lightweight version of Atomify is also available for mobile devices running
Android or iOS.

>>>>

We conclude this case study with a series of simulations of the system described above for different densities $\rho$.
Each simulation runs 10000 timesteps before we export the plots from \code{fix vx} to MATLAB using the Export function seen in Fig. \ref{fig:velocity_profile1}.
All these plots are now merged into a final figure which is shown in Fig. \ref{fig:velocity_profiles}.
It is here evident that the velocity near the boundary is not zero, which is the reason why the permeability is much higher for dilute gases than dense liquids.
This is, as mentioned earlier, called the Klinkenberg effect\citep{klinkenberg1941permeability}.

\section{\label{sec:discussion}Discussion}
In this paper we have presented Atomify, an application that reduces the large amount of context switches and mouse clicks
when creating new simulation scripts.
As of today, only LAMMPS is supported as the physical simulator, but other codes can easily be integrated
due our general implementation with no assumpetion about the underlying code except atom positions.
The communication overhead is minimized since LAMMPS runs in the same process as Atomify, sharing the memory.

\section{\label{sec:future}Future work}
Atomify continues in heavy development and we have several features planned for future versions.
We already have a simple version of Atomify in the web browser using WebGL and WebAssembly.
This makes it easy to test scripts in the browser with all simple functionalities available.
This is especially useful in educational settings where teachers wish to introduce students
to LAMMPS without installing additional software.
It will also serve as a nice demonstration of the full desktop application of Atomify.

\section{Availability}
Atomify is availabe on Linux, MacOS and Windows and can be downloaded from
\href{https://ovilab.net/atomify}{http://ovilab.net/atomify}.
A lightweight version of Atomify is also available for mobile devices running
Android or iOS.
